\documentclass[9pt,letterpaper]{article}
\usepackage[margin=0.55in, bottom=0.4in, top=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{array}

\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue!70!black}

\titleformat{\section}{\small\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{5pt}{2pt}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\tiny\thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\begin{document}

\begin{center}
    {\large\bfseries StarkHacks General Policies \& Agreements}\\[2pt]
    {\footnotesize Purdue University Compliance, Photo Release, and Participant Acknowledgment}
\end{center}

\vspace{2pt}\hrule\vspace{4pt}

All individuals attending StarkHacks (participants, mentors, judges, sponsors, and attendees) are considered visitors to Purdue University and must comply with all applicable university policies in addition to StarkHacks policies.

\section{I. Purdue University \& StarkHacks Policy Compliance}

Attendees agree to abide by all applicable Purdue University visitor policies and all StarkHacks-specific policies (Code of Conduct, Content Policy, Name \& Brand Policy), including but not limited to:
\begin{itemize}[nosep, leftmargin=*, topsep=2pt]
    \item Conduct and community standards; anti-harassment and non-discrimination
    \item Safety and emergency procedures; use of university facilities and spaces
    \item Information technology and network usage
    \item Prohibited activities (e.g., unauthorized solicitation, substance violations)
\end{itemize}

Failure to comply may result in removal from the event and referral to university authorities. Organizers reserve the right to remove any individual at their sole discretion.

\section{II. Photo and Media Release}

This release applies to all individuals attending StarkHacks in any capacity (participants, mentors, judges, sponsors, volunteers, and guests). By attending, each individual grants a perpetual, royalty-free, worldwide, irrevocable license to the authorized parties below to photograph, record, film, or otherwise capture their likeness, voice, image, and participation during StarkHacks.

\textbf{Authorized Parties:}
\begin{itemize}[nosep, leftmargin=*, topsep=2pt]
    \item StarkHacks organizing team
    \item Humanoid Robot Club (HRC) at Purdue University
    \item Purdue University departments, offices, and affiliated organizations (including the College of Engineering, Purdue Research Foundation, and university marketing and communications)
    \item Event sponsors and official partners affiliated with StarkHacks
    \item Major League Hacking (MLH) or any official hackathon league or partner organization
    \item Authorized and credentialed media personnel
\end{itemize}

\textbf{Grant of Rights:} Authorized parties may use, reproduce, edit, adapt, publish, distribute, and display captured media in any format, including social media, websites, press releases, marketing materials, newsletters, presentations, and future event promotions. Media may be shared among the authorized parties above for promotional, educational, or archival purposes. Attendees waive any right to review, approve, or receive compensation for the final use of such materials.

\textbf{Photography by Attendees:} Non-official photographers may photograph or record at StarkHacks provided they obtain consent from any individual captured, avoid private or restricted areas (e.g., restrooms), and immediately honor any request to stop recording or delete images.

\section{III. Acknowledgment and Signature}

By signing below, I confirm I have read and agree to all applicable Purdue University visitor policies, the StarkHacks Code of Conduct, Content Policy, Name \& Brand Policy, and the Photo and Media Release above.

\vspace{5pt}
\noindent
\begin{tabular}{@{}p{0.45\textwidth}@{\hspace{0.08\textwidth}}p{0.47\textwidth}@{}}
\textbf{Full Name (Print)} & \textbf{Date} \\[6pt]
\hrulefill & \hrulefill \\[10pt]
\textbf{Signature} & \\[6pt]
\hrulefill & \\
\end{tabular}

\vspace{4pt}
\noindent\textit{\footnotesize If under 18, a parent or legal guardian must also complete the following:}
\vspace{3pt}

\noindent
\begin{tabular}{@{}p{0.45\textwidth}@{\hspace{0.08\textwidth}}p{0.47\textwidth}@{}}
\textbf{Guardian Full Name (Print)} & \textbf{Date} \\[6pt]
\hrulefill & \hrulefill \\[10pt]
\textbf{Guardian Signature} & \\[6pt]
\hrulefill & \\
\end{tabular}

\vspace{4pt}\hrule\vspace{3pt}

{\tiny\textit{In effect from December 1, 2025. Last updated: April 5, 2026.}}

\end{document}
